---
title: "Introduction to textools"
author: 
  - "Jeffrey Arnold"
  - "Aaron Erlich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: textools.bib
vignette: >
  %\VignetteIndexEntry{Introduction to textools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r head, include=FALSE}
library("tidyverse")
library("textools")

```

# Introduction

The replicable research movement has highlighted the need for researchers to produce numeric and graphical displays of quantitative information directly from code. Many tools exist to output both figures and tables into LaTeX from R. 

However, papers also reference many quantitative (or qualitative) pieces of information throughot the descriptive prose. This text lies outside `\figure` or `\table` environments. Recently @eubank_embrace_2016 suggested in the *Political Methodologist* that each individual piece of information generated directly from code be stored in a separate `.tex` file.

We build on this idea to provide a suite of tools to easily manage all of the quantitative pieces of information for a research paper or presentation in LaTeX. To do so we leverage \LaTeX's macro functionality. We also provided a suite of tools inspired by `htmltools` [@wickham_advanced_2015] to translare R in to LaTex (a Domain Specific Language). This functionality allows researchersto create easily readable and properly escaped LaTex directly from R. 

# 

To create a set of macros for \LaTex we use R's list functionality to create these macros. The simplest way to use `textools` is to use `list_to_macros`. `list_to_macros` requires a `list` object in which the researcher gives each item in the list a name and then exports this list to `.tex` file by providing `list_to_macros` with a prefix for the macro and file to export the macros. 

## Export data to a text file with `list_to_macros`


```{r}
data(mtcars)

#create the file where you will store the macro
MACROS_TEX <- "./vignette_macros.tex"

#create an empty list to store the macro
MACROS <- list()

#careful not use underscores. We recommend camelCase in this situation
MACROS$meanCyl <- round(mean(mtcars$cyl), 2)
MACROS$medianCyl <- median(mtcars$cyl)
MACROS$sdCyl <- round(sd(mtcars$cyl), 2)

cat(list_to_macros(MACROS, prefix = "carSumStat"), file = MACROS_TEX)
```

<<<<<<< HEAD
=======
The contents of the `.tex` file will then look like the following

```{r echo=FALSE, comment=NA}
print(list_to_macros(MACROS, prefix = "carSumStat"))
```

The researcher then includes this set of macros in their main \LaTeX file and can call each macro from within the paper. Such a method allows researchers to easily put all of the evidence 


### LaTeX environment


We could then write our article using our custom macros to reference our individual pieces of information. Each macro has an easily recognizable name, following good programming practice. 
```{r echo = FALSE, comment=NA}
#doesn't work

with_latex(
    "We report on summary statistics from the \\texttt{mtcars} dataset The mean number of cylinders is \\carSumStatmeanCyl, the median is \\carSumStatmedianCyl and the standard deviation is \\carSumStatsdCyl")  %>% cat %>% print
```

## Using R6 Classes

```{r}

with_latex( {
  "\\include{./vignette_macros}"
  begin("document", {
    begin("center", {
      "We report on summary statistics from the \texttt{mtcars} dataset"
      }) }) } ) %>% cat
    
    %n%
  C("this is commented") %l%
    "newline" %n%
    M("1" %/% "2") %n%
    m(.("alpha") %/% .("gamma") %^% 2)
} ) } ) %>% cat

```

## Writing small snippets of LaTeX code in R with `with_latex`
>>>>>>> 29662b13475c4d74cbafc9adc0d0cc8050f5287f
